Proposed Solution

### 2017-01-25 CAV17/secs/intro.tex
stuff

The systems research community has recognized this as an important
problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code. In this paper we propose
a framework for automated verification of configuration files: we are analyzing 
files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
almost a thousand file from github.

@@

Our learning algorithm surmounts all of difficulties present in 
existing tools.  \app implements a learning
algorithm inspired by {\em rule association
learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration  files~\cite{configdataset}. Those are real-world reported misconfigurations. A file in the training set might 
contain several different errors and these errors only appear 
in a small percentage of files. We first translate those file into an 
intermediary typed language. With with every type we associate 
a set of very general templates. The user does not
need to provide any templates, they are internally associated to the types.

 algorithm to learn the generated intermediate representations.
The insight of our design is: every file in the training set
contains several different errors and these errors only appear 
in a small percentage of files. Based on this insight,
we are able, with the help of the probabilistic cutoff, to learn a
set of configuration rules. These rules, in general, specify 
which properties the entries in configuration files need to satisfy. 
One can see this learning process as a way of deriving  
a specification for configuration files.  
Once a specification is obtained, we can do verification that 
uses these learned rules to check the correctness of 
the configuration files
of interest and detect potential errors.

\para{Step~3: Rule graph analysis}
To ensure the learned rules are good enough,
\app employs a further analysis stage to refine the learned rules.
In general, \app builds a graph to model the learned rules,
and analyzes this graph's properties, ranking the importance
and relevance of these rules. Finally, \app outputs
a set of refined rules as the eventual specification
to check the target configuration file $F$.

We have implemented a \app prototype, and evaluated it based on
real-world datasets. In our verification experiments, 
we first use a public configuration dataset~\cite{configdataset}, which
contains 261 incorrect MySQL configuration files, as our
training set. We then use \app to learn rules from this training set
and refine these rules. Finally, we check sophisticated 
errors of real configuration files crawled from github,
and detect many errors in these widely-used configuration files.

>>>>

The systems research community has recognized this as an important
problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code. In this paper we propose
a framework for automated verification of configuration files: we are analyzing 
files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
almost a thousand file from Github.

@@

Our learning algorithm surmounts all of difficulties present in 
existing tools.  \app implements a learning
algorithm inspired by {\em rule association
learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration  files~\cite{configdataset}. Those are real-world reported misconfigurations. A file in the training set might 
contain several different errors and these errors only appear 
in a small percentage of files. We first translate those file into an 
intermediary typed language. With with every type we associate 
a set of very general interfaces. An \app's user does not
need to provide them, they are internally associated to the types. The 
learner then instantiates those interfaces with the keywords appearing in 
the training set. However, since files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are good enough,
\app employs a further analysis to refine the learned rules.
In general, \app builds a graph modeling the learned rules,
and then analyzes this graph to rank the importance
and relevance of the learned rules.

\ruzica{mark, please put here summary of evaluation resuls}

We have implemented a \app prototype, and evaluated it based on
real-world datasets. In our verification experiments, 
we first use a public configuration dataset~\cite{configdataset}, which
contains 261 incorrect MySQL configuration files, as our
training set. We then use \app to learn rules from this training set
and refine these rules. Finally, we check sophisticated 
errors of real configuration files crawled from Github,
and detect many errors in these widely-used configuration files.
